---
pagetitle: "`r paste0('Investments - ', country)`"
title-block: false
---

[Investments - {{< var doc.country >}}]{.fakeh1}

## PRB monitoring

```{r inv_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_inv.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 


## Value of the assets for New Investments included in the Performance Plan `r country` | `r if_else(params$country == params$rp_full, "all ANSPs", paste0(main_ansp, " and comparison with Union-wide"))` 

### Determined and additional asset value by investment category

::: {layout="[ 60, 40 ]"}
:::: {#table_invest_av_type}

```{r table_invest_av_type}
#| file: R/table_invest_av_type.R
#| out.width: "100%"
```

`r if (params$country == params$rp_full) ":::: {.content-hidden}"`

```{r table_invest_av_vs_eu2, eval=(params$country != params$rp_full)}
#| file: R/table_invest_av_vs_eu2.R
#| out.width: "100%"
```

`r if (params$country == params$rp_full) "::::"`

::::

:::: {.chart-container}
```{r chart_invest_av_vs_eu1, eval=(params$country != params$rp_full)}
#| file: R/chart_invest_av_vs_eu1.R
#| out.width: "100%"
```
::::
:::

### Determined asset value: en route and terminal

::: {layout="[ 60, 40 ]"}
:::: {#table_invest_av_er_trm}
```{r table_invest_av_er_trm}
#| file: R/table_invest_av_er_trm.R
#| out.width: "100%"
```
::::

:::: {.chart-container}
```{r chart_invest_av_er_trm}
#| file: R/chart_invest_av_er_trm.R
#| out.width: "100%"
```
::::
:::

### Determined asset value by type of investment

::: {layout="[ 60, 40 ]"}
:::: {#table_invest_av_category}
```{r table_invest_av_category}
#| file: R/table_invest_av_category.R
#| out.width: "100%"
```
::::

:::: {.chart-container}
```{r chart_invest_av_vs_eu3, eval=(params$country != params$rp_full)}
#| file: R/chart_invest_av_vs_eu3.R
#| out.width: "100%"
```
::::
:::

`r if (params$country != params$rp_full) "::: {.content-hidden}"`

```{r chart_invest_av_state_type, eval=(params$country == params$rp_full)}
#| file: R/chart_invest_av_state_type.R
#| out.width: "100%"
```

`r if (params$country != params$rp_full) ":::"`


## Costs related to investments included in the Performance Plan `r country` | `r if_else(params$country == params$rp_full, "all ANSPs", main_ansp)`

### New and existing investments

```{r}
#| label: table_invest_cost_total
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_total.R")
table1
```

```{r}
#| echo: false
table2
```

```{r}
#| echo: false
table3
```

<br>

::: {layout="[ 50, 0, 50 ]"}
:::: {.chart-container}
```{r chart_invest_cost_total}
#| file: R/chart_invest_cost_total.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {.chart-container}
```{r chart_invest_cost_category}
#| file: R/chart_invest_cost_category.R
#| out.width: "100%"
```
::::
:::

`r if (params$country != params$rp_full) "::: {.content-hidden}"`

[Placehoder for chart - missing total costs]

```{r chart_invest_cost_state, eval=(params$country == params$rp_full)}

# <!-- #| file: R/chart_invest_cost_state.R -->
# <!-- #| out.width: "100%" -->

```

`r if (params$country != params$rp_full) ":::"`

### Costs of investments by nature - En route

```{r, options= (cost_type = "en route")}
#| label: table_invest_cost_nature_er
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_nature.R")
table1
```

```{r}
#| echo: false
table2
```

```{r}
#| echo: false
table3
```

<br>

`r if (params$country == params$rp_full) "::: {.content-hidden}"`
::: {layout="[10, 80, 10]"}
:::: {#empty_div}
::::

:::: {.chart-container}
```{r chart_invest_difference_cost_er, eval=(params$country != params$rp_full), options= (cost_type = "en route")}
#| file: R/chart_invest_difference_cost.R
#| out.width: "100%"
```
::::

:::: {#empty_div}
::::
:::
`r if (params$country == params$rp_full) ":::"`

`r if (params$country != params$rp_full) "::: {.content-hidden}"`

```{r chart_invest_difference_cost_country_e, eval=(params$country == params$rp_full), options= (cost_type = "en route")}

# <!-- #| file: R/chart_invest_difference_cost_country.R -->
# <!-- #| out.width: "100%" -->

```

`r if (params$country != params$rp_full) ":::"`



`r if (params$no_tcz == 0 & params$country != params$rp_full) "::: {.content-hidden}"`

### Costs of investments by nature - Terminal

```{r, eval=(params$no_tcz != 0 | params$country == params$rp_full), options= (cost_type = "terminal")}
#| label: table_invest_cost_nature_trm
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_nature.R")
if(table_exists) {
  table1} else {
  cat(paste0(main_ansp, " does not provide ", cost_type, " services", "."))
  }

```

```{r, eval=(params$no_tcz != 0 | params$country == params$rp_full)}
#| echo: false
if(table_exists) {
  table2}
```

```{r, eval=(params$no_tcz != 0 | params$country == params$rp_full)}
#| echo: false
if(table_exists) {
  table3}
```

<br>


`r if (params$country == params$rp_full | params$country == "Sweden") "::: {.content-hidden}"`
::: {layout="[10, 80, 10]"}
:::: {#empty_div}
::::

:::: {.chart-container}
```{r chart_invest_difference_cost_trm, eval=(params$no_tcz != 0 & params$country != params$rp_full & params$country != "Sweden"), options= (cost_type = "terminal")}
#| file: R/chart_invest_difference_cost.R
#| out.width: "100%"
```
::::

:::: {#empty_div}
::::
:::
`r if (params$country == params$rp_full | params$country == "Sweden") ":::"`

`r if (params$no_tcz == 0 & params$country != params$rp_full) ":::"`


`r if (params$country != params$rp_full) "::: {.content-hidden}"`
```{r chart_invest_difference_cost_country_t, eval=(params$country == params$rp_full), options= (cost_type = "terminal")}

# <!-- #| file: R/chart_invest_difference_cost_country.R -->
# <!-- #| out.width: "100%" -->

```
`r if (params$country != params$rp_full) ":::"`



`r if (params$country == params$rp_full) "::: {.content-hidden}"`
### Costs by new major investments

```{r}
#| label: table_invest_cost_new_major
#| out.width: "100%"
#| echo: false

source("R/table_invest_cost_new_major.R")
table1
```

```{r}
#| echo: false
table2
```

```{r}
#| echo: false
table3
```

<br>

```{r no_investment, include=FALSE}
source("R/chart_invest_cost_new_major.R")
no_investments <- no_investments
```

`r if (no_investments <= 6)"::: {.content-hidden}"`
```{r chart_invest_cost_new_major_many, eval=(no_investments > 6)}
#| file: R/chart_invest_cost_new_major.R
#| out.width: "100%"
```
`r if (no_investments <= 6)":::"`



`r if (no_investments > 6)"::: {.content-hidden}"`
::: {layout="[ 10, 80, 10 ]"}
:::: {#empty_div}
::::

:::: {.chart-container}
```{r chart_invest_cost_new_major_few, eval=(no_investments <= 6)}
#| file: R/chart_invest_cost_new_major.R
#| out.width: "100%"
```
::::

:::: {#empty_div}
::::
:::
`r if (no_investments > 6)":::"`
`r if (params$country == params$rp_full) ":::"`


### Costs by Common Project One (CP1) ATM Functionality (AF)

```{r}
#| label: table_invest_cost_cp1
#| out.width: "100%"
#| echo: false
#| results: asis

source("R/table_invest_cost_cp1.R")
if (identical(table1, "")) {
  cat("No costs associated to CP1.")
} else {
  print(table1)
}
```

```{r}
#| echo: false
#| results: asis

if (identical(table2, "")) {
  cat("")
} else {
  print(table2)
}
```

```{r}
#| echo: false
#| results: asis

if (identical(table3, "")) {
  cat("")
} else {
  print(table3)
}
```


<br>

### Costs by Strategic Deployment Objective (SDO)

```{r}
#| label: table_invest_cost_sdo
#| out.width: "100%"
#| echo: false
#| results: asis

source("R/table_invest_cost_sdo.R")
if (identical(table1, "")) {
  cat("No costs associated to SDOs.")
} else {
  print(table1)
}
```

```{r}
#| echo: false
#| results: asis

if (identical(table2, "")) {
  cat("")
} else {
  print(table2)
}
```

```{r}
#| echo: false
#| results: asis

if (identical(table3, "")) {
  cat("")
} else {
  print(table3)
}
```

<br>

## Expected benefit and impact per new major investment `r country` | `r if_else(params$country == params$rp_full, "all ANSPs", main_ansp)`

`r if (params$country == params$rp_full) "::: {.content-hidden}"`

```{r table_invest_type, eval=!(params$country == params$rp_full)}
#| file: R/table_invest_type.R
#| out.width: "100%"
```

`r if (params$country == params$rp_full) ":::"`

<br>

::: {layout="[ 50, 0, 50 ]"}
:::: {.chart-container}
```{r chart_invest_type_eu}
#| file: R/chart_invest_type_eu.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {.chart-container}
```{r chart_invest_type}
#| file: R/chart_invest_type.R
#| out.width: "100%"
```
::::
:::


## Public funding granted for total CAPEX (CEF/TEN-T)



`r if (params$country == params$rp_full) "::: {.content-hidden}"`
::: {layout="[ 50, 0, 50 ]"}
:::: {.chart-container}
```{r chart_invest_funding_year}
#| file: R/chart_invest_funding_year.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::: {.chart-container}
```{r chart_invest_funding_vs_eu}
#| file: R/chart_invest_funding_vs_eu.R
#| out.width: "100%"
```
::::
:::
`r if (params$country == params$rp_full) ":::"`


`r if (params$country != params$rp_full) "::: {.content-hidden}"`
::: {layout="[ 10, 80, 10 ]"}

::::{#empty_div}
::::

:::: {.chart-container}
```{r chart_invest_funding_year_ses}
#| file: R/chart_invest_funding_year.R
#| out.width: "100%"
```
::::

::::{#empty_div}
::::

:::

`r if (params$country != params$rp_full) ":::"`
