::: {.grid .align-items-center}
:::: {.g-col-9}
[Annual Monitoring Report `r toupper(params$year_folder)` - Network Manager]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}</span>
::::
:::

*`r pp_version`*

## Safety (Network Manager - `r rp_full` area)

### Effectiveness of Safety Management (EoSM) (KPI#1) and ATFM overdeliveries (PI#1)

::: {#container-saf1}
:::: {#chart-eosm class="mychart"}

::::: {layout="[ 99, 1 ]"}
:::::: {.chart-container}  

```{r chart-eosm}
#| file: R/chart_level1_saf_nm.R
#| out.width: "99%"
```
::::::

:::::: {#empty-div}
::::::
:::::
<br>

```{r chart-deliveries}
#| file: R/chart_level1_saf_deliveries_nm.R
#| out.width: "99%"
```
::::

:::: {#concl-eosm}

```{r saf_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_saf.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 
::::
:::

## Environment (Network Manager - `r rp_full` area)

### The en route flight efficiency improvement (KPI#1) and Route extension (PI#1)

::: {#container-env style="clear: both"}

:::: {#chart-env class="mychart"}
```{r chart-env-kea, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "99%"
```
::::

:::: {#concl-env}

```{r env_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_env.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-cap style="clear: both"}

## Capacity (Network Manager - `r rp_full` area)
<!-- empty line to ensure next heading leaves enough space -->
<!-- <div style="height: 1px"></div> -->

### The en route ATFM delay savings (KPI#1) and the arrival ATFM delay savings (KPI#2)

:::: {#chart-cap class="mychart"}
```{r chart-cap-er}
#| file: R/chart_level1_cap_er_nm.R
#| out.width: "99%"
```

<br>

```{r chart-cap-trm}
#| file: R/chart_level1_cap_trm_nm.R
#| out.width: "99%"
```

### Other performance indicators (PIs#1-3)

::::: {layout="[ 98, 2 ]"}
:::::: {.chart-container}  

```{r table-cap-pis-nm}
#| file: R/table_level2_cap_pis_nm.R
#| out.width: "99%"
```
::::::

:::::: {#empty-div}
::::::
:::::

::::

:::: {#concl-cap}

```{r cap_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-cef style="clear: both"}
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Cost-efficiency (Network Manager - `r rp_full` area)

### The unit cost for the execution of the tasks (KPI#1)

:::: {#chart-cef class="mychart"}
```{r chart-cef}
#| file: R/chart_level1_cef_nm.R
#| out.width: "99%"
```
::::

:::: {#concl-cef}

```{r cef_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cef.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::