
```{r chart_eosm, include=FALSE}
#| file: R/chart_level1_saf_nm.R
#| out.width: "100%"
```

```{r chart_deliveries, include=FALSE}
#| file: R/chart_level1_saf_deliveries_nm.R
#| out.width: "100%"
```


```{r chart_cap_er, include=FALSE}
#| file: R/chart_level1_cap_er_nm.R
#| out.width: "100%"
```

```{r chart_cap_trm, include=FALSE}
#| file: R/chart_level1_cap_trm_nm.R
#| out.width: "100%"
```


```{=tex}
\setlength{\fboxrule}{0pt} % Set the border width to 0pt (no border)
\setlength{\fboxsep}{0pt} % Remove padding
```

# OVERVIEW

*`r pp_version`*

## Safety (Network Manager - `r rp_full` area)

### Effectiveness of Safety Management (EoSM) (KPI#1) and ATFM overdeliveries (PI#1)

`r layout_2fig("chart_eosm", "chart_deliveries")`

```{r saf_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_saf.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 


\needspace{2\baselineskip}

## Environment (Network Manager - `r rp_full` area)

### The en route flight efficiency improvement (KPI#1) and Route extension (PI#1)

```{r chart_env_kea, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```


```{r env_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_env.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{2\baselineskip}

## Capacity (Network Manager - `r rp_full` area)

### The en route ATFM delay savings (KPI#1) and the arrival ATFM delay savings (KPI#2)

`r layout_2fig("chart_cap_er", "chart_cap_trm")`

```{r table-cap-pis-nm}
#| file: R/table_level2_cap_pis_nm.R
#| include: false
```

### Other performance indicators (PIs#1-3)

``` {r table-cap-pis-nm-p}
#| echo: false
#| results: asis
 
data_prep_pdf <- data_prep_pdf %>%
  mutate(across(everything(), ~ tidyr::replace_na(as.character(.x), "NA"))) |> 
  rename(` ` = pi)

cat(make_quarto_latex_table(
  title = NA,
  df = data_prep_pdf ,
  col_align = "lrrrrr",
  col_widths = c(65, rep(7, 5))
))

```

```{r cap_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{2\baselineskip}

## Cost-efficiency (Network Manager - `r rp_full` area)

### The unit cost for the execution of the tasks (KPI#1)

```{r chart_cef}
#| file: R/chart_level1_cef_nm.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r cef_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cef.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 


